Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-31 Draft/Draft.Rmd
Intro

[Explain what macro-descriptors have found i.e. Bascompte, and what pairwise interactions descriptors have accomplished i.e. trait-matching. End explaining Benno simmons work]

Exploring the different and most frequent motifs could help our understanding of species interactions due to motifs consider direct and indirect interactions not accounted in single species metrics. [Explain this: https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/1365-2435.13736 and say we don't know how motif distribution really looks like in the real world. Which is the expected pattern?]

However, motifs are abstract representations often decoupled from species ecology. [explain here the importance of relating reproductive strategies and pollinators behaviours to their positions within a motif. This is interesting because bridges pairwise interactions to the emergent network via motifs]

@@

all_position_percentiles <- add_study_id(all_position_percentiles)
str(all_position_percentiles)
head(all_position_percentiles)

@@

@@

>>>>

Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. Motifs are cosidered the building blocks that depict subsets of interactions of the network. The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions of plant-pollinator networks in natural systems.

Motifs are abstract representations often decoupled from species ecology.

[explain here the importance of relating reproductive strategies and pollinators behaviours to their positions within a motif. This is interesting because bridges pairwise interactions to the emergent network via motifs]

@@

all_position_percentiles <- add_study_id(all_position_percentiles)
#str(all_position_percentiles)
#head(all_position_percentiles)

@@

**TABLES**

@@

**FIGURES**
